---
title: "Marriage Data: A Temporal Analysis"
subtitle: "Marriage Licenses Over Time"
author: 
  - Kevin Roe
thanks: "Code and data are available at: https://github.com/Kanghyunroe/marriage_license"
date: today
date-format: long
abstract: "The paper analyzes the number of marriage licenses over time. Using R, we analyze the data and found no key insights worth analyzing."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(tinytex)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

The paper analyzes marriage license data sourced from Open Data Toronto [@opendatatoronto]. We used R [@R] to analyze the data.The graph plots the number of marriage licenses filled for each date. From my initial analysis, there doesn't seem to be a clear pattern to analyze and shows some problems I have with the data set. 


# Data {#sec-mydatasection}


```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```



# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


